\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Muhammad Iqbal} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+62-896-9077-2452 \\ Samarinda, ID} 
\address{\href{mailto:iqoqacola@gmail.com}{iqoqacola@gmail.com} \\ \href{https://www.linkedin.com/in/muhammad-iqbal-506a8624b/}{linkedin} \\ \href{https://iqoqacola.github.io/}{iqoqacola.github.io}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{PROFILE}

{I am a Front End Developer with a focus on modern web development, specializing primarily in using React to build dynamic and responsive user interfaces. I possess a strong understanding of frontend development using React and modern JavaScript.}


\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\textbf{Video Editor} \hfill March, 2021 - Now\\
Freelance \hfill \textit{Samarinda, ID}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Accept video editing projects from a variety of clients, including companies, individuals, and marketing agencies.
     \item Edit and compile visual and audio material to create videos that meet client needs.
    \item Ensure projects are completed according to established deadlines, with a focus on quality and client satisfaction. 
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECT}
\vspace{-1.25em}

\item \textbf{PORTFOLIO WEB} {As a skilled developer, I have successfully designed and implemented a dynamic portfolio project utilizing cutting-edge technologies, including React, Sass, Tailwind CSS, and Vite. This project not only showcases my proficiency in these technologies but also emphasizes my commitment to creating visually appealing and performant web applications.  \href{https://iqoqacola.github.io/anime-list/}{(iqoqacola.github.io)}}

\item \textbf{LANDING PAGE} {This project involves the development of a landing page optimized using React as the primary framework, Bootstrap as the CSS framework, and Vite as the fast development tool. This landing page is designed to create an engaging and responsive user experience, with the main goal of increasing visitor conversion to customers.}

\item \textbf{ANIVERSE} {The ANIVERSE project is developed using React, Tailwind CSS, and Vite. This project serves as a platform for users to discover and search for both released and upcoming anime based on various categories. It harnesses the AniList API with GraphQL capabilities to provide comprehensive anime information. The primary objective of the ANIVERSE project is to offer users an intuitive and efficient means to explore anime content. By leveraging the AniList API, users can access a vast database of anime titles, details, and categories. The project aims to enhance user engagement by providing seamless navigation and robust search functionalities. In the creation of this project I Successfully developed an easy-to-use platform for discovering and exploring anime content, catering to the preferences of anime fans. \href{https://iqoqacola.github.io/anime-list/}{(Try it here)}}

\item \textbf{TIC TAC TOE.} {Completed the mini project "Tic Tac Toe" using the React library. This project reflects my ability to implement basic React concepts to build a responsive and dynamic user interface.}

\item \textbf{CALCULATOR.} {I have successfully executed a mini project to create a calculator using the React library, Sass for styling, Tailwind CSS for utility-first styling, and Vite as the build tool. This project showcases my proficiency in integrating multiple technologies for a comprehensive web development experience.}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	INTERNSHIP SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Internship} 
\textbf{House Keeping} \hfill Jun, 2022 - Sep, 2022\\
The Rich Hotel \hfill \textit{Penajam Paser Utara, ID}
 \begin{itemize}
    \itemsep -3pt {} 
     \item After graduating from high school, I decided to undertake an internship in the hotel industry by joining The Rich Hotel in the Housekeeping division.
     \item As a housekeeping intern at The Rich Hotel, I held primary responsibilities for ensuring the cleanliness and comfort of hotel rooms.
    \item Identified and implemented strategies to enhance cleaning process efficiency, reducing the time required for each room without compromising quality.
 \end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Front End Web Development}, DICODING \hfill {January 2024 -}\\
Online coding training program aimed at enhancing the competency of the Indonesian\\ community in the field of information technology.

{\bf Back-End Developer}, DICODING \hfill {March 2024 -}\\
Back-End certification training scholarship program from AWS in the field of Back-End\\ development with global standards.

{\bf Health Promotion}, Poltekkes Kemenkes Kaltim \hfill {Expected 2026}\\
Delving into the concepts and practices of health promotion at the Health Polytechnic\\ of the Ministry of Health in East Kalimantan.

{\bf MIPA}, SMAN 5 PPU \hfill {2019 - 2022}\\
 Engaged in rigorous academics and extracurriculars including advanced coursework\\ and participation in boxing, student council, and community service projects.\\ Developed leadership, teamwork, and communication skills for future pursuits.

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Linux CLI, HTML, CSS, JavaScript, Bootstrap, Tailwind, Git, Github \\ & Sass, JQuery, React, Node.js, Vite, Webpack, RestFull API\\
Soft Skills & Communication, Teamwork, Problem-Solving, Time Management
\end{tabular}\\

\end{rSection}

% %----------------------------------------------------------------------------------------
% %	ACHIEVEMENT SECTION
% %----------------------------------------------------------------------------------------

% \begin{rSection}{Extra-Curricular Activities} 
% \begin{itemize}
%     \item 	Actively write \href{https://www.faangpath.com/blog/}{blog posts} and social media posts (\href{https://www.tiktok.com/@faangpath}{TikTok}, \href{https://www.instagram.com/faangpath/?hl=en}{Instagram}) viewed by over 20K+ job seekers per week to help people with best practices to land their dream jobs. 
%     \item	Sample bullet point.
% \end{itemize}


% \end{rSection}

% %----------------------------------------------------------------------------------------
% %	LEADERSHIP SECTION
% %----------------------------------------------------------------------------------------

% \begin{rSection}{Leadership} 
% \begin{itemize}
%     \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
% \end{itemize}


% \end{rSection}


\end{document}
